### 2021-12-04 text/outline/draft.tex
enable submission via sbatch

We implement several statistical accelerations (that possibly are independently useful) to bring the cost of GLM-EIV down to within about an order of magnitude of the thresholding method. Finally, we develop a Docker-containerized application to deploy GLM-EIV at-scale across tens or hundreds of nodes on clouds (e.g., Microsoft Azure) and high-performance clusters. Leveraging this application, we apply GLM-EIV to analyze two recent, large-scale, high multiplicity-of-infection single-cell CRISPR screen datasets, yielding new biological and statistical insights.

@@

To our knowledge, this is the first statistical work to study single-cell CRISPR screens. One of our objectives is to bring to the attention of the statistical community an emerging class of functional genomics assays that likely will exert a major impact on biology research. Additionally, this is the first work to leverage the ondisc-Nextflow-cloud/HPC technology stack, a powerful and user-friendly set of tools for large-scale single-cell analysis that other researchers (especially statisticians) likely will find useful.

>>>>

We implement several statistical accelerations (that possibly are of independent utility) to bring the cost of GLM-EIV down to within about an order of magnitude of the thresholding method. Finally, we develop a Docker-containerized application to deploy GLM-EIV at-scale across tens or hundreds of nodes on clouds (e.g., Microsoft Azure) and high-performance clusters. Leveraging this application, we apply GLM-EIV to analyze two recent, large-scale, single-cell CRISPR screen datasets. % In highly noisy settings ; by contrast, in less noisy settings, GLM-EIV serves as a principled and reproducible threshold selection procedure.

@@

To our knowledge, this is the first statistical work to study single-cell CRISPR screens. One of our objectives is to bring to the attention of the statistical community an emerging class of functional genomics assays that likely will exert a major impact on biology research. Additionally, this is the first work to leverage the ondisc-Nextflow-cloud/HPC technology stack, a set of programming tools for large-scale single-cell analysis that we view as powerful and user-friendly.
